---
title: "Reveal.js Format Test"
subtitle: "Comprehensive Component Testing"
format:
  mcanouil-revealjs:
    extensions:
      mcanouil:
        debug-borders: true
engine: knitr
---

# Introduction

## About This Test

:::: {.fragment fragment-index="1"}

This presentation tests all components of the mcanouil Reveal.js format.

:::

- [Title slide styling with corner brackets.]{.fragment fragment-index="2"}
- [Section slides with banner style.]{.fragment fragment-index="3"}
- [Gradient underlines on headings.]{.fragment fragment-index="4"}
- [Code blocks and annotations.]{.fragment fragment-index="5"}

## About This Test

Here we go again.

## Hiding From Menu and TOC {.unlisted}

This slide should not appear in the menu or table of contents.

## Features Being Tested

1. Custom title slide partial.
2. Section slide detection.
3. Subsection outline generation.
4. Date superscript formatting.
5. Menu/logo visibility.

# Typography

## Heading Levels

### Level 3 Heading

This tests the gradient underline on different heading levels.

#### Level 4 Heading

Level 4 headings should not have underlines.

## Text Formatting

Regular paragraph text using **Alegreya Sans** font.

- **Bold text** for emphasis.
- *Italic text* for titles.
- `Inline code` styling.
- [Links](https://mickael.canouil.fr) inherit colours.

## Lists

Unordered list:

- First item.
- Second item.
- Third item with longer text to test wrapping behaviour.

Ordered list:

1. First step.
2. Second step.
3. Third step.

# Code Examples

## Basic Code Block

```r
# R code example
library(ggplot2)

ggplot(mtcars) +
  aes(x = mpg, y = wt) +
  geom_point() +
  theme_minimal()
```

## Code with Line Highlighting

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: "|1|2-3|4-6"
# Step-by-step code reveal
data <- mtcars
data[["efficiency"]] <- data[["mpg"]] / data[["wt"]]

ggplot(data) +
  aes(x = efficiency, y = hp) +
  geom_point()
```

## Python Example

```python
import polars as pl
from plotnine import ggplot, aes, geom_point

# Load and transform data
df = pl.read_csv("data.csv")
df = df.with_columns(
    (pl.col("value") * 2).alias("doubled")
)
```

## Code Annotations

```{r}
#| eval: false
#| echo: true
library(dplyr) # <1>

mtcars |> # <2>
  filter(mpg > 20) |> # <3>
  select(mpg, cyl, hp) |> # <4>
  arrange(desc(mpg)) # <5>
```

1. Load the dplyr package for data manipulation.
2. Start with the mtcars dataset.
3. Filter rows where mpg is greater than 20.
4. Select only the columns we need.
5. Sort by mpg in descending order.

## Tabset Example

::: {.panel-tabset}

### R Code

```{r}
#| eval: false
#| echo: true
# R implementation
library(ggplot2)

ggplot(mtcars) +
  aes(x = mpg, y = wt) +
  geom_point()
```

### Python Code

```python
# Python implementation
from plotnine import ggplot, aes, geom_point
from plotnine.data import mtcars

(
    ggplot(mtcars)
    + aes(x="mpg", y="wt")
    + geom_point()
)
```

### Output

The plot shows the relationship between fuel efficiency (mpg) and weight (wt).

:::

# Callouts and Blocks

## Callout Examples

::: {.callout-note}
This is a note callout to highlight important information.
:::

::: {.callout-warning}
This is a warning callout for cautionary messages.
:::

::: {.callout-tip}
This is a tip callout for helpful suggestions.
:::

## Blockquotes

> "The best way to predict the future is to invent it."
>
> --- Alan Kay

## Columns Layout

:::: {.columns}

::: {.column width="50%"}
**Left Column**

Content on the left side of the slide.
:::

::: {.column width="50%"}
**Right Column**

Content on the right side of the slide.
:::

::::

# Tables and Data

## Simple Table

| Package | Purpose | Language |
|---------|---------|----------|
| ggplot2 | Visualisation | R |
| polars | Data manipulation | Python |
| Quarto | Publishing | Multiple |

## Data Summary

```{r}
#| echo: false
#| eval: true
summary(mtcars[, 1:4])
```

# Visual Elements

## Images

When using images, they should be centred and properly sized.

## Incremental Reveals

::: {.incremental}
- First point appears.
- Then the second.
- Finally the third.
:::

## Fragments

::: {.fragment}
This appears first.
:::

::: {.fragment}
This appears second.
:::

::: {.fragment}
This appears third.
:::

## Line Highlighting with Fragments

:::: {.fragment fragment-index="3"}
Step 3
:::

:::: {.columns}

:::: {.column width="50%"}

```{.r code-line-numbers="|2|3" code-line-fragment-indices="1,2,4"}
par(mfrow = c(1, 2))
plot(cars)
plot(cars, col = "red")
par(mfrow = c(1, 1))
```

:::

:::: {.column width="50%"}

```{.r code-line-numbers="|2|3" code-line-fragment-indices="1,2,4"}
par(mfrow = c(1, 2))
plot(cars)
plot(cars, col = "red")
par(mfrow = c(1, 1))
```

:::

:::

:::: {.fragment fragment-index="1"}
First step
:::

# Background Variations

## Testing Section Styles

The plugin supports three section slide styles:

1. **Banner** (default): Heading in a banner at 20% from top.
2. **Full**: Centred heading with full inverted background.
3. **Minimal**: Simple centred heading.

## Background Effects

Available background effects:

- **Solid**: Plain inverted colour.
- **Gradient**: Linear gradient (default).
- **Pattern**: Dots, diagonal lines, or grid.

# Conclusion

## Summary

This test presentation covers:

- Title slide with author metadata.
- Section slides with outlines.
- Typography and text formatting.
- Code blocks with syntax highlighting.
- Callouts and special blocks.
- Tables and data display.
- Incremental reveals and fragments.

## Next Steps

1. Render the presentation.
2. Check all components visually.
3. Test light and dark modes.
4. Verify PDF export.

## Thank You

Questions?

Website: [mickael.canouil.fr](https://mickael.canouil.fr)

GitHub: [github.com/mcanouil](https://github.com/mcanouil)
